US Korea Exchange Rates \\ STA206 Final Project

### 2014-12-14 paper.tex
sequence numbering, final draft

\[
    Y = -0.69 c_1 \frac{G_{K}}{G_{US}}
    -0.25 c_2 \frac{E_{K}}{E_{US}}
    +0.59 c_3 \frac{R_{K}}{R_{US}}
    +0.29 c_4I_{K} - 0.30 c_5 I_{US} + \epsilon.
\]

The 95\% confidence interval does not include 0 for any of these variables,
so we are 95\% confident that these signs are correct. Since the predictor variables
are scaled or ratios they are unitless. Now the model has a
natural interpretation. Suppose that the Korean economy grows while the US
economy remains stagnant. Then the exchange rate should decrease, because
the Korean Won will have more value relative to the US Dollar.
From our model we can infer the following:

@@

Common sense and economic reasoning tells us that all of these should be
true. The data and analysis confirm our intuition. Perhaps with the use of
time series techniques this analysis could be extended.

Returning to out original questions, the results of this analysis suggest
that if you want to exchange your currency
to foreign currency, it would be better to do it when your home country's 
GDP is good, or the exports are good, or the inflation is relatively lower.

@@

\section{Appendix - Reproducibility}

\section{Appendix 1}

@@

\section{Appendix 2}

\subsection{Model Selection Output}
\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrrr}
		\hline
		& sse & bic & r2 & r2a & cp \\
		\hline
		1 & 0.00 & -46.47 & 0.37 & 0.37 & 411.04 \\
		2 & 0.00 & -178.62 & 0.80 & 0.79 & 55.28 \\
		3 & 0.00 & -185.95 & 0.82 & 0.81 & 41.04 \\
		4 & 0.00 & -206.51 & 0.85 & 0.85 & 13.91 \\
		5 & 0.00 & -212.36 & 0.86 & 0.86 & 5.39 \\
		6 & 0.00 & -210.43 & 0.87 & 0.86 & 4.72 \\
		7 & 0.00 & -207.14 & 0.87 & 0.86 & 5.33 \\
		8 & 0.00 & -202.47 & 0.87 & 0.86 & 7.22 \\
		9 & 0.00 & -197.85 & 0.87 & 0.86 & 9.06 \\
		10 & 0.00 & -193.12 & 0.87 & 0.86 & 11.00 \\
		\hline
	\end{tabular}
\end{table}

@@

>>>>

\[
    Y = Intercept -c_1 \frac{G_{K}}{G_{US}}
    -c_2 \frac{E_{K}}{E_{US}}
    +c_3 \frac{R_{K}}{R_{US}}
    +c_4I_{K} - c_5 I_{US} + \epsilon.
\]

The 95\% confidence interval does not include 0 for any of these variables,
so we are 95\% confident that the signs of the coefficients are correct. Since the predictor variables
are scaled or ratios they are unitless. Now the model has a
natural interpretation. Suppose that the Korean economy grows while the US
economy remains stagnant. This should be associated with a decreasing
exchange rate, because
the Korean Won will have more value relative to the US Dollar.
From our model we can infer the following:

@@

Common sense and economic reasoning tells us that all of these statements should be
true. The data and analysis confirm our intuition. Perhaps with the use of
time series techniques this analysis could be extended.

Now we return to our original questions. The results of this analysis 
suggest a reasonable course of action if you want to exchange your currency
to foreign currency. In relative terms, it is better to do it when your home country's 
GDP is high, or the exports are high, or the inflation is lower.

@@

\section{Appendix 1 - Plots}

@@

\newpage
.
\newpage

\section{Appendix 2 - R Output}

\subsection*{Model Selection Output}
\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrrr}
		\hline
		& sse & bic & r2 & r2a & cp \\
		\hline
		1 & 0.00 & -46.47 & 0.37 & 0.37 & 411.04 \\
		2 & 0.00 & -178.62 & 0.80 & 0.79 & 55.28 \\
		3 & 0.00 & -185.95 & 0.82 & 0.81 & 41.04 \\
		4 & 0.00 & -206.51 & 0.85 & 0.85 & 13.91 \\
		5 & 0.00 & -212.36 & 0.86 & 0.86 & 5.39 \\
		6 & 0.00 & -210.43 & 0.87 & 0.86 & 4.72 \\
		7 & 0.00 & -207.14 & 0.87 & 0.86 & 5.33 \\
		8 & 0.00 & -202.47 & 0.87 & 0.86 & 7.22 \\
		9 & 0.00 & -197.85 & 0.87 & 0.86 & 9.06 \\
		10 & 0.00 & -193.12 & 0.87 & 0.86 & 11.00 \\
		\hline
	\end{tabular}
\end{table}

@@

\section{Appendix 3 - Reproducibility}
